---
title: "Week 1 Weekend Homework"
output: html_notebook
---
```{r}
library(tidyverse)
```

```{r}
books <- read_csv("data/books.csv")
```

```{r}
dim(books)
```

```{r}
str(books)
```

```{r}
names(books)
```

```{r}
glimpse(books)
```

```{r}
books %>%
  # mutate(average_rating = case_when(
  #   ratings_count <= 5 ~ "NA",
  #   text_reviews_count <= 5 ~ "NA",
  #   TRUE ~ average_rating
  #   
  # ))
  
  mutate(average_rating = na.if(ratings_count <= 5)) %>%
  mutate(average_rating = na.if(text_reviews_count <= 5))

# Here I am attempting to mutate away the average ratings where ratings count or
# text reviews count is less than 5, as this skews the average rating, giving 
# misrepresenting data for average_rating
```



# Now that we have had a look at the data some questions come to mind that may be answered.

# Question 1: Find out the 10 most widely used publishers in the data set.

```{r}
books %>%
  
  # select(publisher, authors, bookID) %>%
  # count(publisher)
  
  # group_by(publisher, authors, bookID) %>%
  # summarise(publisher, sum(n()))
  
  group_by(publisher) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 10)

# Got there eventually! Now I have the publishers in descending order of how many books were published with each. 

```

# Question 2: Usings ratings_count as a proxy for popularity, are older books more popular than newer books? 

```{r}
books_date_edited <- books %>%
  select(title, ratings_count, text_reviews_count, publication_date) %>%
  mutate(date = as.Date(publication_date, "%m/%d/%Y")) %>%
  arrange(date)

books_date_edited
# current form of the date does not read properly. Need to mutate the publication date into something more in line with how we can arrange the dataset.

# No way! Actually managed to use stackoverflow to mutate the date function.
```

# Question 3: Which 100 authors have the highest average rating, across all of their books?

```{r}
average_author_ratings <- books %>%
  select(authors, average_rating, ratings_count) %>%
  group_by(authors) %>%
  # aggregate(authors_ratings[, 2:3], list(authors_ratings$authors), mean)
  mutate(average_author_rating = mean(average_rating)) %>%
  arrange(desc(average_author_rating)) %>%
  filter(ratings_count > 1000) %>%
  head(100)

average_author_ratings

# Data is heavily skewed by authors who have a handful of ratings, but these are not representative. Added a filter to get these results out.

# How do I condense down the authors to single variables, new table?
  
  
```

# Question 4: My friend Greg is looking for a new book to read and is looking for something specific. He doesn't want a book written after the year 1980, as he likes to get lost in a world prior to the internet. He wants to be able to read it while on holiday, so the book has to be between 500 - 1200 pages long. He wants something highly rated (above a 8/10), has a few reviews he can read before purchasing (>10), but not too popular as he loves being alternative (1000 < ratings_count < 10,000).

```{r}
books %>%
  mutate(date = as.Date(publication_date, "%m/%d/%Y")) %>%
  mutate(average_rating = average_rating * 2) %>%
  filter(date < "1980-01-01") %>%
  filter(num_pages >= 500, num_pages <= 1200) %>%
  filter(average_rating >= 4.00) %>%
  filter(text_reviews_count >= 10) %>%
  filter(ratings_count < 10000, ratings_count > 1000) %>%
  arrange(desc(average_rating))
  
```

# Question 5: Combine the average_rating and ratings_count to form a new variable with a qualitative edge

```{r}
books %>%
  select(ratings_count, average_rating) %>%
  mutate(book_rating_category = case_when(
    ratings_count >= 50000 & average_rating >= 4.5 ~ "Blockbuster",
    ratings_count <= 50000 | average_rating >= 4.0 ~ "Underground Hit",
    TRUE ~ "Other"
  )) %>%
  arrange(book_rating_category)
```



