---
title: "weekend_homework"
author: "Jonny Nelson"
date: "11/12/2021"
output: html_document
---

```{r}
library(e1071)
library(tidyverse)
library(janitor)
library(prob)
library(infer)
data(msleep)
```

# Question 1 - Explore the data set

```{r}
glimpse(msleep)
```
```{r}
head(msleep, 100)
```

# Question 2 - Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

# Visualise the data

```{r}
msleep %>%
  ggplot(aes(x = sleep_total)) +
  geom_boxplot()
```

# Observed mean in the sample

```{r}
observed_stat <- msleep %>%
  summarise(mean_sleep_total = mean(sleep_total))

observed_stat
```

# Null distribution

```{r}
null_distribution <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesise(null = "point", mu = 7) %>%
  
  # "mu" is the population mean
  
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
```

# Visualising the Bootstrap Test

```{r}
null_distribution %>%
  visualise(bins = 30) +
  xlab("mean sleep total") +
  shade_p_value(obs_stat = observed_stat$mean_sleep_total,
                direction = "left")
```

# p-value

```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat$mean_sleep_total,
              direction = "left")

p_value
```

# Question 3 - Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

# Data for omnivores and herbivores

```{r}
unique(msleep$vore)

omnivores <- msleep %>%
  dplyr::filter(vore == "omni") %>%
  select(vore, sleep_total)

herbivores <- msleep %>%
  dplyr::filter(vore == "herbi") %>%
  select(vore, sleep_total)
```

# Apend the two data sets

## Here we are going to assume that the two variables are independent

## H0: mu-sleep_total(omni) - mu-sleep_total(herbi) == 0
## HA: mu-sleep_total(omni) - mu-sleep_total(herbi) > 0

## Significance level alpha  = 0.05

```{r}
proportions_data <- bind_rows(omnivores, herbivores, .id = "vore") %>%
  mutate(vore = if_else(vore == "1",
                            "omni",
                            "herbi"))
```

# Visualise the new data

```{r}
proportions_data %>%
  ggplot(aes(x = vore, y = sleep_total)) +
  geom_boxplot()
```


# Null Distribution

```{r}
null_distributions <- proportions_data %>%
  specify(sleep_total ~ vore) %>%
  hypothesise(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means",
            order = c("omni", "herbi"))

null_distributions
```

# Observed Stat

```{r}
observed_stat <- proportions_data %>%
  specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means",
            order = c("omni", "herbi"))

observed_stat
```

# Visualising the Null Distribution

```{r}
null_distributions %>%
  visualise(bins = 30) +
    shade_p_value(obs_stat = observed_stat,
                  direction = "right")
```

# Calculating the p_values

```{r}
p_value <- null_distributions %>%
  get_p_value(obs_stat = observed_stat,
             direction = "right")

p_value

# Not a significant p-value observed therefore fail to reject the null hypothesis.
```



# Question 4 - Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.


```{r}
animals_domesticated <- msleep %>%
  select(conservation, )
  mutate(vore = if_else(vore == "1",
                            "omni",
                            "herbi"))
```

