---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
library(janitor)
```

```{r}

cardbase <- read_csv("data/CardBase.csv")

customer_base <- read_csv("data/CustomerBase.csv")

transaction_base <- read_csv("data/TransactionBase.csv")

fraud_base <- read_csv("data/FraudBase.csv")

```

```{r}
carbase_data <- cardbase %>%
  janitor::clean_names()
```

```{r}
customer_base_data <- customer_base %>%
  janitor::clean_names()
```

```{r}
transaction_base_data <- transaction_base %>%
  janitor::clean_names()
```

```{r}
fraud_base_data <- fraud_base %>%
  janitor::clean_names()
```

# From looking at all these data sets, the column names need to be brought to be all lowercase. Used the janitor to help out.

# Question 2: Join the data containing card details and customer details by customer id, so that all records of card details and any matching records in customer details are kept. Before you run the code, think about how many rows you expect to see after joining.


```{r}
left_join(carbase_data, customer_base_data, by = "cust_id")

# We only have 500 observations in tge cardbase_data, so this will limit the left_join to spit out new data of only 500 observations, even though there are over 5000 observations in customer_base_data
```

# Question 3: Join the data containing fraud details with transaction details so all rows of both tables are kept. What does the resulting row number tell you?

```{r}

full_join(fraud_base_data, transaction_base_data)

# joined all observations of using "transaction_id" as the primary key. most observations do not have a fraudulent flag, therefore most transactions are genuine.
```

# Question 4: Join the data containing card details with transaction details so rows from the first which have matching ones in the second are returned, but only return rows in the first table once.

```{r}

semi_join(carbase_data, transaction_base_data, by = c("card_number" = "credit_card_id"))

```

# Question 5: Read in hat_observations and separate observation into two columns, hat_colour and hat_type.

```{r}
hat_observations <- read_csv("data/hat_observations.csv")
```

```{r}

hat_observations %>%
  separate(observation, c("hat_colour", "hat_type"), sep = "," ) %>%
  unite(date, c("day", "month", "year"), sep ="/") %>%
    mutate(date = as.Date(date, "%d/%m/%Y"))
  

```

# Question 6: Unite day, month, and year columns into a column called date using a suitable separator. Then find the date where the most berets were observed. 

# See above for answer. 



