---
title: "homework_attempt"
author: "Jonny Nelson"
date: "26/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(GGally)
library(janitor)
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(corrplot)

customers <- read_csv("data/mall_customers.csv") %>%
  clean_names()

head(customers)

# Used range and unique functions to find information below
```

# Data Exploration

## Understanding the Variables

* #### customer_id - anonamous identifier
* #### gender - Male and Female
* #### age - 18 to 70
* #### annual_income_k - 15K - 137K
* #### spending_score - 1 to 99

## Initial visualisations 

### Ggpairs

```{r}
ggpairs(customers)
```
* #### Spending score is not correlated to customer_id as expected but also not annual income, which is more suprising.
* #### age has a low negative correlation with spending score of - 0.327 and gender appears to have some minor differences

### Spending Score vs Age

```{r}
customers %>%
  ggplot() +
  geom_col(aes(x = age, y = spending_score_1_100), bins = range(customers$age), fill = "steel blue")
```

* #### Can see a normal distribution in the spending score assigned to different ages. 
* #### Increasing from 18 and then topping out at around 32 until slowly declining until 70.

### Spending Score vs Gender

```{r}
customers %>%
  ggplot() +
  geom_jitter(aes(x = gender, y = spending_score_1_100), bins = range(customers$age), fill = "steel blue", width = 0.02)
```

```{r}
customers %>%
  ggplot() +
  geom_boxplot(aes(x = gender, y = spending_score_1_100), bins = range(customers$age), fill = "steel blue", width = 0.1)
```

* #### Spending scores for men and women are remarkably similar. 
* #### However, men do have a slighly lower 75th percentile and 25th percentile compared to women, so they do in this population, spend slightly less.

# K-Means Clustering

## Normalising the Data

```{r}
customers_clean <- customers %>%
  select(-customer_id) %>%
  mutate(across(where(is.numeric), scale),
         across(where(is.character), as.factor)) %>%
  select(spending_score_1_100, age, gender, annual_income_k)

# summary(customers_clean)
```

## K-Means Clustering

```{r}
set.seed(9)
library(purrr) 

max_k <- 20 

customers_scale <- customers_clean %>%
  select(annual_income_k, spending_score_1_100)

k_clusters <- tibble(k = 2:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(customers_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, customers_scale)
  )

k_clusters
```

